\documentclass[11pt,a4paper,sans]{moderncv}

% moderncv themes
\moderncvtheme[green]{classic}                  % optional argument are 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'roman' (for roman fonts, instead of sans serif fonts)
%\moderncvtheme[green]{classic}                % idem

% character encoding
\usepackage[utf8]{inputenc}                   % replace by the encoding you are using
% Multi-column layout for languages and technical skills
\usepackage{multicol}
% adjust the page margins
\usepackage[scale=0.87]{geometry}
\usepackage{amsfonts}
%\setlength{\hintscolumnwidth}{3cm}						% if you want to change the width of the column with the dates
%\AtBeginDocument{\setlength{\maketitlenamewidth}{6cm}}  % only for the classic theme, if you want to change the width of your name placeholder (to leave more space for your address details
%\AtBeginDocument{\recomputelengths}                     % required when changes are made to page layout lengths

% Hyperlinks
%\usepackage{hyperref}								% to use hyperlinks
%\definecolor{linkcolour}{rgb}{0,0.2,0.6}			% hyperlinks setup
%\hypersetup{colorlinks,breaklinks,urlcolor=linkcolour, linkcolor=linkcolour}

% personal data
\name{Gonzalo}{Barrera Borla}
\phone[mobile]{+54~(9~11)~4082~6338}                   % optional, remove / comment the line if not wanted
\email{gonzalobb@gmail.com}                               % optional, remove / comment the line if not wanted
\homepage{github.com/capitantoto}                         % optional, remove / comment the line if not wanted

%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------
\begin{document}
%-----       resume       ---------------------------------------------------------
\makecvtitle

\vspace{-0.5cm}


\section{Selected Industry Experience}

\cventry{2021 -- Current}{Engineer Manager, Data Science}{Jampp @ Affle Group}{Remote}{}{After becoming SME on our statistical learning systems, I moved \emph{slightly} away from coding to technical management. Emphasis is set on sketching lines of research for continuous improvement of our bidding strategy from a theoretical standpoint, that small dedicated teams can then further on their own.}

\cventry{2019 -- 2020}{Senior Data Scientist}{Jampp}{Buenos Aires, AR}{}{I researched, developed and monitored supervised models for classification tasks in the programmatic advertising market. Servicing predictions for 2M QPS, we developed sampling techniques to learn from extremely imbalanced (1000:1 or worse), massive (1T+ rows) datasets within exacting performance constraints.}


\cventry{2016 -- 2019}{Expert Data Analysis Advisor}{Chief of the Ministerial Cabinet Office}{Buenos Aires, AR}{}{I worked for the \emph{Dirección Nacional de Datos} in designing, developing and managing a BI platform to integrate data from the federal government's core management systems. I had both technical (data model \& ETL pipelines' design) and product-oriented responsibilities, such as defining objectives with stakeholders. I contributed to \href{https://code.iadb.org/repository/31/pydatajson}{\color{blue}{pydatajson}}, a python library selected by the IADB's ``\href{https://code.iadb.org/repository/31/pydatajson}{\color{blue}{Code for Development}}'' FOSS program.}


\cventry{2013 -- 2016}{Business Data Analyst}{Official Nascar Members' Club}{Buenos Aires, AR; Charlotte, NC, USA}{}{I mostly did assorted analysis and report automation for all company teams. I also helped Marketing with rigorous hypothesis' testing of their A/B tests, and Finance by running credit fraud detection models.}

\section{Selected Academic Experience}

\cventry{H2 2021}{External Professor}{Fac. de Ingeniería, Fac. de Cs. Exactas, UBA}{Argentina}{}{I taught ``Machine Learning in Graphs'' for the masters' degree on Data Mining program. We provided longtime R users with an in-depth first course on Python for graph data science. We recorded lectures for asynchronous watching and led synchronous classes with heavy emphasis on practice. All of the material is publicly available on \href{https://youtube.com/playlist?list=PL1WsZAYeCpYUA-k5Ry5O803GpipEnoFQk}{\color{blue}{YouTube}} and \href{https://github.com/fcen-amateur/aa-en-grafos}{\color{blue}{GitHub}}, and covers `networkx', `igraph' and `neo4j', as well as the scientific python stack.}

\cventry{2012 -- 2017}{Junior Mathematical Olympiad Coach}{Various schools}{Buenos Aires, Argentina}{}{}



\cventry{2006 -- 2016}{Private tutor}{}{Buenos Aires, Agentina}{}{I taught Mathematics, Physics and Chemistry for elementary to undergraduate-level students.}



\cventry{2012 -- 2015}{Teaching Assistant}{Facultad de Cs. Económicas; Universidad de Buenos Aires}{Argentina}{}{I taught ``Statistics II'', a senior-year class on Hypothesis Testing and Generalized Linear Models.}



\section{Education}
\cventry{2017 -- 2021}{MSc in Statistics}{Facultad de Ciencias Exactas y Naturales - UBA}{}{}{GPA: 10.0 (10.0 scale). My thesis (in progress, due July 2022) uses the \emph{Fermat distance}, a graph-based approach to distance estimation on $d$-dimensional manifolds embedded in $\mathbb{R}^D\ (d\ll D)$ to produce a kernel density estimation on the manifold, which can then be used for classification tasks.}
\cventry{2009 -- 2014}{Licenciatura en Econom\'ia (BA + MA in Economics)}{Facultad de Cs. Económicas - UBA}{}{}{GPA: 8.94 (10.0 scale). Graduated \emph{magna cum laude}, as valedictorian of my class. My masters' thesis, \emph{The Limits of Electoral Predictability}, is publicly available on GitHub (\href{https://github.com/capitantoto/tesis_mesis/blob/master/ruby/programa.rb}{\color{blue}{code}} and \href{https://github.com/capitantoto/tesis_mesis/blob/master/texes/tesis.pdf}{\color{blue}{essay}}).}


\section{Languages}

\begin{minipage}{\maincolumnwidth}
  \begin{multicols}{2}
    \cvlanguage{Spanish}{Native speaker}{}
    \cvlanguage{French}{Advanced}{}

    \columnbreak


    \cvlanguage{English}{Bilingual {\scriptsize \emph{CPE (CEFR C2), 2008. Grade: A}}}{}
    \cvlanguage{Portuguese}{Advanced}{}

  \end{multicols}
\end{minipage}


\section{Courses}

\begin{minipage}{\maincolumnwidth}
  \begin{multicols}{2}
    \cvlanguage{AWS}{\href{https://www.aws.training/Transcript/CompletionCertificateHtml?transcriptid=a7vdggmA406jSwdQN6YTjA2}{\color{blue}{Architecting on AWS}}}{}

    \columnbreak


    \cvlanguage{Coursera}{\href{https://www.coursera.org/account/accomplishments/verify/5BJS2WRBAMWB}{\color{blue}{Machine Learning}}, with Andrew Nguyen}{}

  \end{multicols}
\end{minipage}

% \section{Interests}

%\cvitem{Science Olympiads}{I participated in several Science Olympiads throughout high school. I obtained three silver medals in the National Chemistry Olympiad (2006-2008), as well as a 2nd place in the National Mathematic Olympiad (2005), and silver medals in the "Olimpiada Matematica Rioplatense" (2006) and "Olimpiada Matematica del Cono Sur" (2007)}
% \cvitem{Machine Learning}{I completed Stanford's ``Machine Learning'' course by Andrew Nguyen on Coursera, about contemporary machine learning techniques. [\href{https://www.coursera.org/account/accomplishments/certificate/5BJS2WRBAMWB}{{\color{blue}{link to certificate}}}]}



% \cvitem{Science Olympiads}{I participated throughout high school in Mathematical and Chemistry Olympiads, consistently obtaining top finishes at national (chemistry) and international (mathematics) events.}



%\cvitem{Intellectual Property}{I gave a talk entitled \emph{Reflections on the Epistemology of Intellectual Property}, analyzing the effects that IP rights have on the development of art, culture, science and technology. Presented at the XVIII ``Jornadas de Epistemología de las Ciencias Económicas'', Universidad de Buenos Aires, 2012.}

%

%\cvitem{Personal}{In my spare time, I binge on second hand books, spend the nights cooking and eating with my girlfriend Victoria or play the guitar in the park while Molly & Nina, our dogs, run merrily around.}

\end{document}
